Enforced Invariant Confluence

### 2018-03-05 doc/paper_redux/stratified_iconfluence.tex
Added more to stratified invariant-confluence.

  \item
    Transaction processing is a bit different. Imagine a processor $p_i$ in
    state $s_i$ with pair $(I_j, T_j)$ active wants to execute transaction $t$.
    %
    If $t \in T_j$, then $p_i$ executes $t_i$ so long as doing so maintains
    $I_j$.
    %
    If $t \notin T_j$, then $p_i$ initiates a round of coordination among the
    processors. All processors adopt state state $s = s_1 \join \cdots \join
    s_n$. Then, all processors execute $t$. If $t(s)$ does not satisfy $I$,
    then the processors remain in state $s$ and continue normal processing.  If
    $t(s)$ does satisfy $I$, then the processors enter state $t(s)$ and choose
    pair $(I_k, T_k)$ to active where $(I_k, T_k)$ is the first pair in $P$
    where $I_k(t(s))$.
\end{itemize}

@@

\todo{Describe why this scheme ensures ``Iconfluence''}.

>>>>

  \item
    Transaction processing is a bit different. Imagine a processor $p_i$ in
    state $s_i$ with pair $(I_j, T_j)$ active wants to execute transaction $t$.
    %
    If $t \in T_j$, then $p_i$ executes $t_i$ so long as doing so maintains
    $I_j$.
    %
    If $t \notin T_j$, then $p_i$ initiates a round of coordination among the
    processors. All processors adopt state state $s = s_1 \join \cdots \join
    s_n$. Then, all processors execute $t$. If $t(s)$ does not satisfy $I$,
    then the processors remain in state $s$ and continue normal processing.  If
    $t(s)$ does satisfy $I$, then the processors enter state $t(s)$ and choose
    pair $(I_k, T_k)$ to active where $(I_k, T_k)$ is the first pair in $P$
    where $I_k(t(s))$ (which is guaranteed to exist since $\cup_i I_i = I$).
\end{itemize}

@@

Stratified invariant-confluence, like invariant-confluence, guarantees that no
replica ever enters a state that violates the invariant $I$. How does it
guarantee this?
%
Initially, all processors begin in the same state $s$ and with the same active
pair $(I_j, T_j)$, and this invariant is maintained whenever a global
coordination is run. During normal non-coordinated operation, because $O$ is
\sticonfluent{s}{T_j}{I_j}, $\setst{s'}{\stireachable{s}{T_j}{I_j}{s'}}
\subseteq I_j \subseteq I$. Thus, processors stay within $I_j$ which itself
lies within $I$. During a coordinated action, processors transition to state $s
= s_1 \join \cdots \join s_n \in I_j$ and then possibly transition into a new
state $t(s)$ with new active pair $(I_k, T_k)$.

A couple things to note:
\begin{itemize}
  \item
    If $O$ is \sTIconfluent{}, then we can let $P = (I, T)$.

  \item
    Let $P = (I, T')$ where $T' \subseteq T$. This is a special case of the
    token-based approach in~\cite{gotsman2016cause} where every transaction in
    $T - T'$ acquires a single token $\tau$ and every transaction in $T$
    doesn't acquire any token. The token-based approach
    in~\cite{gotsman2016cause} is not completely subsumed by our stratified
    invariant-confluence. For example, stratified invariant-confluence cannot
    emulate multi-token systems. Conversely, stratified invariant-confluence is
    not subsumed by the token-based approach which cannot stratify $I$. Notably
    though, the token-based approach can adjust what tokens a transaction
    acquires based on its state, but this is not used in the paper.
\end{itemize}
